---
title: "Mapping The Spatial Patterns of Internal Migration in Europe"
author: "[Francisco Rowe](http://www.franciscorowe.com) [[`@fcorowe`](http://twitter.com/fcorowe)]<sup>1*</sup>, Nikos Patias[[`@pat_nikos`](https://twitter.com/pat_nikos)]<sup>1</sup>"
output: html_document
---

<sup>1</sup> *Geographic Data Science Lab, University of Liverpool, Liverpool, United Kingdom*

<sup>*</sup> *Corresponding author*:
F.Rowe-Gonzalez@liverpool.ac.uk

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(mapdeck)
library(htmlwidgets)
library(htmltools)
library(widgetframe)
knitr::opts_chunk$set(collapse = TRUE)
```

**Abstract**
Internal migration has replaced fertility and mortality as the primary demographic process shaping the spatial distribution of populations within countries. While a rich comparative literature has examined the intensity, composition and spatial impacts of population movement in Europe, the spatial structure of internal migration flows is less well understood. We present a flow map of internal migration flows within European countries using the most recent data available. The graphic reveals the predominant role of capital cities in the internal migration system, and distinctive patterns of internal migration fostering population concentration in Northern, Central and Eastern Europe, and population deconcentration in Western and Southern Europe.

**Keywords**: internal migration flows, Europe, mapping, Mapbox

The map below displays the largest internal migration flows in each country by mapping flows greater than 1,000, or top 5% flows in countries where the largest flow is smaller than 1,000.

```{r, include=FALSE}
#read mapdeck object
flowmap_EU <- readRDS(file = "./data/flowmap_mapdeckobj.rds")

flowmap_EU
#frameWidget(flowmap_EU, options = frameOptions(allowfullscreen = TRUE))
```

